\cvsection{Projects}

\begin{cventries}

  \cventry
  {Course Project - CS665}
  {\href{https://github.com/mayanksha/CS665-RA}{HackTheL3}}
  {\emph{\texttt{\href{https://github.com/mayanksha/CS665-RA}{github://mayanksha/CS665-RA}}}}
  {September, 2019}
  {
    \begin{cvitems}
    \item A Research Project on Reverse-Engineering the Cache Replacement Policy of L3 Cache, using various cache-set and slice aware data-access patterns.
    \end{cvitems}
  }

  \cventry
  {E-Cell, IITK}
  {SIP Portal}
  {}
  {December 2017}
  {
    \begin{cvitems}
    \item An Automation Portal which acts as a channel amongst Startups, Students and College for facilitating Internships. 
    \item Actively used by SIP, IITK since two years with 500+ Student Registrations each year.
    \end{cvitems}
  }

  \cventry
  {Microsoft Codefundo++}
  {Alertify}
  {\emph{\texttt{\href{https://github.com/vinayaktrivedi/alertify}{github://vinayaktrivedi/alertify}}}}
  {Oct'2018}
  {
    \begin{cvitems}
      \item A Web App on Django, to Alert users about impending disasters in real-time based on their locations, using Text-processing methods like Stemming, Keyword Extraction and Sentiment Analysis on Tweets. 
      \item \textbf{Runner-up in Microsoft Codefundo++ 2018.}
    \end{cvitems}
  }

  \cventry
  {Course Project - CS252}
  {Bhagvada Geeta ChatApp}
  {}
  {October 2018}
  {
    \begin{cvitems}
    \item A Mobile app to display the Geeta-shlokas relevant to your problem query, using various NLP Techniques and 7-dimensional representation of Shlokas on 7-sins. 
    \end{cvitems}
  }

  \smallcventry
  {An Interpreter for Oz}
  {Ozit}
  {written in Oz.}
  {Sept'2019}
  {{\emph{\texttt{\href{https://github.com/vinayaktrivedi/ozit}{github://Ozit}}}}}
  {}

  \smallcventry
  {Compiler for Golang}
  {Gorakshak}
  {written in Python.}
  {Jan'2019}
  {{\emph{\texttt{\href{https://github.com/vinayaktrivedi/GOrakshak}{github://GOrakshak}}}}}
  {}

  \smallcventry
  {Course Project}
  {GemOS}
  {Operating Systems}
  {Aug'2018}
  {{\emph{\texttt{\href{https://github.com/vinayaktrivedi/gemOS}{github://https://gemOS}}}}}
  {}

  \smallcventry
  {NodeJs+PHP backend based}
  {VAAD SAMVAAD}
  {Social Networking website.}
  {Jan'2018}
  {{\emph{\texttt{\href{https://github.com/vinayaktrivedi/facebook-copy}{github://facebook\_copy}}}}}
  {}

  \smallcventry
  {A cryptographically Secure Cloud Storage Web App}
  {Cloud2.0}
  {written in Golang.}
  {}
  {{\emph{\texttt{\href{https://github.com/vinayaktrivedi/Cloud2.0}{github://Cloud2.0}}}}}
  {}

\end{cventries}
\vspace{-1mm}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../cv.tex"
%%% TeX-engine: xelatex
%%% End: